
\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
I would first like to thank my thesis advisor Prof. dr. Rineke (L.C.) Verbrugge of the Artificial Intelligence and Cognitive Engineering (ALICE) research institute at Groningen University. The little time she has, due to the sudden growth of the department, was unnoticeable. She always took the time to listen to my difficulties and/or problems and gave optimal advice. She consistently allowed this paper to be my own work, and slightly steered me in the right the direction whenever I needed it.

Furthermore, I would like to thank Youri de Koster who has supported me at the office. His weekly reviews and personal advices have taught me more than any class and thesis ever could. Also Rob Goes, Dennis Kersten and Edwin Knoop have been a great aid, and continued to support me, even when I thought I could not continue.

I would also like to thank the experts who were involved in this research project: Ronghuo Zheng, Mathijs de Weerdt, and Tim Baarslag. Without their input, no thesis would have been written.

I would also like to acknowledge my fellow interns, especially Marnix Montantus and Pedram Muurlink, who always made the internship even more enjoyable and the 09:30 hr coffee is forever in my mind. Furthermore, I would like to thank my friends for their continuous support.

I must express my deep gratitude to my mother, sister and brother, and to my dearest Vivianne for providing me with constant support and endless encouragement throughout my years of study and through the process of researching and writing this thesis. This achievement would not have been possible without them. Finally, I would like to thank my father, who has always been the greatest support during the studies, and unfortunately cannot see what has been accomplished.

Diederik van Krieken
\end{abstract}